%%%%%%%%%%%%Outline%%%%%%%%%%%%%%%%%%

%%%
% message<kernel extensions like eBPF are used for performance and safety critical applications>
% xx

%%%
% message<many optimization opportunities are not used>
% - compared to llvm, current BPF JIT is not well optimized

%%%
% message<inherent tradeoff>
% implement optimization is heavy
% kernel code is safety sensitive
% so it is impractical to implement optimization in the kernel

%%%
% message<idea is to ==内核提供机制，用户态提供 策略==>
% idea is to separate optimization policy and kernel

%%%
% message<we propose a dynamic, extensible framework for compiling and optimizing eBPF>
% design:
% - kinsn: this is the most important!
% - userspace daemon: program analysis, optimization, and code rewriting
% - kernel component: verification and in-place recompilation
% advantages:
% - usability: transparent to eBPF developers
% - flexibility: enable flexible, dynamic optimization policies
% - correctness: minimal invasion (fewer than 600 lines of code)
% - safety: uphold the eBPF safety model

%%%
% message<evaluation shows that our tool is more light-weight and achieves better performance>
% effectiveness: 
% - performance: outperform baseline on various workloads
% - code size: reduce binary size
% - huge runtime overhead reduction, small dynamic re-compilation cost
% generalizability: two arch (x86, ARM)

% comment from yusheng: 
% 内核 很慢 ，因为 security issue 很多，修改很复杂

%%%%%%%%%%%%Outline%%%%%%%%%%%%%%%%%%

\begin{abstract}

Linux increasingly uses eBPF programs to run networking, tracing, and security logic on hot kernel paths.
Each eBPF program is verified and JIT-compiled only once, during loading, so a loaded program cannot later be revised with runtime information.
That limitation matters because many useful transformations become profitable or necessary only after observing a running workload.
A natural response is to move richer recompilation logic into the kernel, but that approach would enlarge trusted kernel code and would tie fast-changing policy to safety-critical implementation.
We present \tool, a system that separates recompilation policy from kernel mechanism for loaded eBPF programs.
A userspace daemon selects rewrites, the existing verifier checks safety, the JIT emits machine code, and a small kernel mechanism installs the new version only after verification and JIT compilation succeed.
This separation supports specialization and hardening after loading without changing existing loaders or attachment points.
Experiments with microbenchmarks and real applications show smaller native code, higher end-to-end performance, and low online overhead.
Safety case studies show that invalid rewrites are rejected and that failed recompilation leaves the original program running.

\end{abstract}