%%%%%%%%%%%%Outline%%%%%%%%%%%%%%%%%%

%%%
% message<xx>
% xx

%%%%%%%%%%%%Outline%%%%%%%%%%%%%%%%%%

\section{Design}
\label{sec:design}

% TODO: Rewrite Design section for v2 architecture.
% The v2 design is based on three components:
%   Component 1: Kernel syscall extensions (BPF_PROG_GET_ORIGINAL + BPF_PROG_REJIT)
%   Component 2: kinsn -- platform-specific instruction extensions via inline kfuncs
%   Component 3: Userspace daemon (discovery, analysis, rewriting, profiling)
% See plan doc §4 for full architecture diagram and details.
% Key differences from v1:
%   - REJIT accepts complete new BPF bytecode (not a policy blob / patch)
%   - Kernel runs full bpf_check() + JIT on new bytecode (full re-verification)
%   - kinsn via KF_INLINE_EMIT reuses existing kfunc verifier (zero verifier changes)
%   - ~600 LOC kernel changes (down from ~6400 in v1)
%   - Daemon is Rust, zero libbpf dependency, raw BPF syscall only

\textsc{BpfReJIT} introduces a dynamic, extensible compilation
framework for kernel eBPF through a three-component architecture that
embodies a microkernel-inspired separation of concerns.

\subsection{Architecture Overview}
\label{sec:architecture}

\textit{[TODO: Full v2 architecture description with three-component
diagram. See plan doc \S4.1--4.4 for the authoritative design.]}

\subsection{Component 1: Kernel Syscall Extensions}
\label{sec:syscall}

\textit{[TODO: BPF\_PROG\_GET\_ORIGINAL and BPF\_PROG\_REJIT syscall
extensions. REJIT accepts complete new BPF bytecode, runs full
bpf\_check() + JIT, atomically swaps JIT image on the same struct
bpf\_prog. Fail-safe: verification failure changes nothing.]}

\subsection{Component 2: kinsn --- Platform-Specific Instruction Extensions}
\label{sec:kinsn}

\textit{[TODO: kinsn mechanism via inline kfuncs (KF\_INLINE\_EMIT).
Kernel modules register kinsn with verification semantics + JIT emit
callbacks. Reuses kfunc verifier, BTF type system, module lifecycle.
Graceful degradation to function call when module not loaded.]}

\subsection{Component 3: Userspace Daemon}
\label{sec:daemon}

\textit{[TODO: Daemon workflow: enumerate live programs via
BPF\_PROG\_GET\_NEXT\_ID, retrieve original bytecode via
BPF\_PROG\_GET\_ORIGINAL, analyze + rewrite bytecode (may insert kinsn
calls), submit via BPF\_PROG\_REJIT. Compilation passes informed by
runtime profiling. Rust implementation, zero libbpf dependency.]}

\subsection{Security Model}
\label{sec:security}

\textit{[TODO: Safety/correctness separation. Kernel verifier guarantees
safety (identical to BPF\_PROG\_LOAD). Daemon responsible for
correctness (semantic preservation). Fail-safe: verify failure changes
nothing. Privilege: CAP\_BPF required.]}
